---
title: "R Notebook"
output: html_notebook
---

##

```{r}
library(dplyr)
library(here)
library(ggplot2)
library(lubridate)
library(data.table)
library(ggrepel)
load(here("data", "results.RData"))
```


```{r}
temp <- read.table(here("data", "predatory_journals.txt"), sep="\t", header=FALSE)

predj <- tibble(
    journal1 = gsub("\\s*\\([^\\)]+\\)","",as.character(temp$V1)) %>% tolower(),
    key1=1:length(journal1)
)

mrj <- subset(abstracts, !duplicated(journal), select=c(journal)) %>% mutate(key2=1:length(journal), journal=gsub("\\s*\\([^\\)]+\\)","",as.character(journal)) %>% tolower())

library(fedmatch)

temp <- merge_plus(data1 = mrj, data2 = predj, by.x="journal", by.y="journal1", match_type="fuzzy", unique_key_1="key2", unique_key_2="key1")

head(temp)
dim(temp$matches)



mrj$predatory <- mrj$journal %in% temp$matches$journal
table(mrj$predatory)
abstracts$journal <- gsub("\\s*\\([^\\)]+\\)","",as.character(abstracts$journal)) %>% tolower()
abstracts$predatory <- abstracts$journal %in% temp$matches$journal

group_by(abstracts, year=year(pub_date)) %>%
    summarise(n=n(), npred=sum(predatory)) %>%
    mutate(prop=npred/n, sem = sqrt(npred * (n-npred)/n^3), lci = pmax(0, prop - (1.96 * sem)), uci = pmin(prop + (1.96 * sem), 1)) %>%
    ggplot(., aes(x=year, y=prop, ymin=lci, ymax=uci)) + geom_line() + geom_ribbon(alpha=0.2) + theme(legend.position="bottom") + xlim(2005,2024) +
    geom_text(aes(label=npred), vjust=-1) +
    scale_x_continuous(breaks=seq(2005,2024,1), limits=c(2005, 2024)) +
    theme(axis.text.x=element_text(angle=45, hjust=1)) +
    labs(y="Proportion of papers in predatory journals", x="Year")
```


## Countries

```{r}
countries <- fread(here("data", "countries.csv"), header=FALSE)
authors2 <- left_join(authors, countries, by=c("country"="V1"))
authors2$country <- authors2$V2

authors2$country[authors2$country == "USA"] <- "United States"
authors2$country[authors2$country == "The Netherlands"] <- "Netherlands"

authors2 <- authors2 %>% mutate(country2 = case_when(
    country == "United Kingdom" ~ "UK",
    country == "United States" ~ "USA",
    country == "China" ~ "China",
    # country == "Sweden" ~ "Sweden",
    # country == "Germany" ~ "Germany",
    # country == "Australia" ~ "Australia",
    # country == "Canada" ~ "Canada",
    # country == "The Netherlands" ~ "The Netherlands",
    # country == "Denmark" ~ "Denmark",
    # country == "South Korea" ~ "South Korea",
    TRUE ~ "All other countries"
))

table(authors2$country2)

temp <- authors2 %>%
    filter(!duplicated(pmid)) %>% inner_join(., subset(abstracts, select=c(pmid, pub_date)), by="pmid") %>%
    group_by(country2, year=year(pub_date)) %>%
    summarise(n=n()) 
data_ends <- filter(temp, year == "2024")

temp_all <- authors2 %>%
    filter(!duplicated(pmid)) %>% inner_join(., subset(abstracts, select=c(pmid, pub_date)), by="pmid") %>%
    group_by(country, year=year(pub_date)) %>%
    summarise(n=n())


temp %>%
    ggplot(., aes(x=year, y=n, colour=country2)) + 
    # geom_smooth(se=FALSE) + 
    geom_line() +
    geom_point(data=data_ends, aes(x=year, y=n, colour=country2)) +
    geom_text_repel(
        aes(label = country2), data = data_ends
    ) +
   scale_y_log10() +
   xlim(2005,2024) +
   theme(legend.position="none")
```

Plot understanding exponential growth

```{r}
    temp %>%
        ggplot(., aes(x=year, y=n, colour=country2)) + 
        # geom_smooth(se=FALSE) + 
        geom_line() +
        geom_point(data=data_ends, aes(x=year, y=n, colour=country2)) +
        geom_text_repel(
            aes(label = country2), data = data_ends
        ) +
    xlim(2005,2024) +
    theme(legend.position="none") +
    labs(y="Number of papers", x="Year")
ggsave("country.pdf", width=8, height=4)
```

## Paper mills

```{r}
paper_mill <- tibble(perc=c(0.92, 0.02, 0, 0.06), country2=c("China", "USA", "UK", "All other countries"))
temp <- left_join(temp, paper_mill, by="country2")
temp$n_adj <- temp$n * (1 - temp$perc)
data_ends <- filter(temp, year == "2024")
temp %>%
    ggplot(., aes(x=year, y=n_adj, colour=country2)) + 
    # geom_smooth(se=FALSE) + 
    geom_line() +
    geom_point(data=data_ends, aes(x=year, y=n_adj, colour=country2)) +
    geom_text_repel(
        aes(label = country2), data = data_ends
    ) +
   xlim(2005,2024) +
   theme(legend.position="none") +
   labs(y="Relative number of papers adjusted for paper mills", x="Year")

```

Retraction watch paper mill papers

```{r}
format_date <- function(x) {
    do.call(rbind, strsplit(x, " "))[,1] %>% gsub("/", "-", .) %>% as.Date(., format="%m-%d-%Y") %>% lubridate::year()
}

format_country <- function(x) {
    case_when(grepl("China", x) ~ "China", grepl("United States", x) ~ "USA", grepl("United Kingdom", x) ~ "UK", TRUE ~ "All other countries")
}

rw <- read.csv("~/Downloads/retraction_watch.csv")

# split the Country column by ";" and duplicate the row for every country
dim(rw)
rw <- rw %>% tidyr::separate_rows(Country, sep=";")

table(rw$Country)

pm <- paper_milly <- rw %>% filter(grepl("paper mill", Reason, ignore.case=TRUE)) %>%
    mutate(year=format_date(OriginalPaperDate), country2 = format_country(Country)) %>%
    group_by(year, country=Country) %>% summarise(nret=n())

left_join(temp_all, pm) %>%
    mutate(nret = ifelse(is.na(nret), 0, nret)) %>%
    filter(year < 2023) %>%
    ggplot(., aes(x=nret, y=n, colour=year, group=country)) + geom_point() + geom_line(aes(group=country))

left_join(temp_all, pm) %>%
    mutate(nret = ifelse(is.na(nret), 0, nret)) %>%
    filter(country == "China" & year < 2023) %>%
    ggplot(., aes(x=nret, y=n, colour=year)) + geom_point() + geom_line()
```


```{r}
paper_milly <- rw %>% filter(grepl("paper mill", Reason, ignore.case=TRUE)) %>%
    mutate(year=format_date(OriginalPaperDate), country2 = format_country(Country)) %>% 
    group_by(year, country2) %>% summarise(nret=n())

paper_mill_y <- group_by(paper_milly, year) %>% summarise(nret_all=sum(nret))
paper_milly <- left_join(paper_milly, paper_mill_y, by="year") %>% mutate(percrety=nret/nret_all)
ggplot(paper_milly, aes(x=year, y=nret, colour=country2)) + geom_line() + geom_point() + theme(legend.position="bottom") + labs(y="Proportion of papers in paper mills", x="Year") + scale_colour_brewer(type="qual") + xlim(2015,2022)

temp <- left_join(temp, paper_milly, by=c("year"="year", "country2"="country2"))
temp$percrety[is.na(temp$percrety)] <- 0

temp$n_adjy <- temp$n * (1 - temp$percrety)
data_ends <- filter(temp, year == "2023")
temp %>%
    ggplot(., aes(x=year, y=n_adj, colour=country2)) + 
    # geom_smooth(se=FALSE) + 
    geom_line() +
    geom_point(data=data_ends, aes(x=year, y=n_adj, colour=country2)) +
    geom_text_repel(
        aes(label = country2), data = data_ends
    ) +
   xlim(2005,2023) +
   theme(legend.position="none", ) +
   labs(y="Relative number of papers adjusted for paper mills", x="Year")

temp %>%
    ggplot(., aes(x=year, y=n_adjy, colour=country2)) + 
    # geom_smooth(se=FALSE) + 
    geom_line() +
    geom_point(data=data_ends, aes(x=year, y=n_adjy, colour=country2)) +
    geom_text_repel(
        aes(label = country2), data = data_ends
    ) +
   xlim(2005,2023) +
   theme(legend.position="none") +
   labs(y="Relative number of papers adjusted for paper mills", x="Year")
```

```{r}
temp %>%
    group_by(year) %>%
    summarise(n=sum(n), n_adjy=sum(n_adjy)) %>%
    tidyr::pivot_longer(cols=c(n, n_adjy), names_to="type", values_to="value") %>%
    ggplot(., aes(x=year, y=value)) + 
    # geom_smooth(se=FALSE) + 
    geom_line(aes(colour=type)) +
   xlim(2005,2023) +
   labs(y="Relative number of papers adjusted for paper mills", x="Year")

```



## China universities

```{r}
c211 <- readLines(here("data", "211_universities.txt"))
table(c211 %in% authors2$institution)

inst <- subset(authors2, !duplicated(institution), institution) %>% mutate(key1=1:n())
c211 <- tibble(c211=c211, key2=1:length(c211))

c985 <- readLines(here("data", "985_universities.txt"))
table(c985 %in% authors2$institution)

c985 <- tibble(c985=c985, key2=1:length(c985))

ctemp_211 <- merge_plus(data1 = inst, data2 = c211, by.x="institution", by.y="c211", match_type="fuzzy", unique_key_1="key1", unique_key_2="key2")
authors2$c211 <- authors2$institution %in% ctemp_211$matches$institution

ctemp_985 <- merge_plus(data1 = inst, data2 = c985, by.x="institution", by.y="c985", match_type="fuzzy", unique_key_1="key1", unique_key_2="key2")
authors2$c985 <- authors2$institution %in% ctemp_985$matches$institution
table(authors2$country == "China", authors2$c211)
table(authors2$country == "China", authors2$c985)
```

```{r}
authors2$country3 <- authors2$country2
authors2$country3[authors2$country3 == "China" & !authors2$c211] <- "China (other)"
authors2$country3[authors2$country3 == "China" & authors2$c211] <- "China (211)"

authors2$country4 <- authors2$country2
authors2$country4[authors2$country4 == "China" & !authors2$c985] <- "China (other)"
authors2$country4[authors2$country4 == "China" & authors2$c985] <- "China (985)"

table(authors2$country3)
table(authors2$country4)
```


```{r}
temp <- authors2 %>%
    filter(!duplicated(pmid)) %>% inner_join(., subset(abstracts, select=c(pmid, pub_date)), by="pmid") %>%
    group_by(country3, year=year(pub_date)) %>%
    summarise(n=n()) 
data_ends <- filter(temp, year == "2023")

temp %>%
    ggplot(., aes(x=year, y=n, colour=country3)) + 
    # geom_smooth(se=FALSE) + 
    geom_line() +
    geom_point(data=data_ends, aes(x=year, y=n, colour=country3)) +
    geom_text_repel(
        aes(label = country3), data = data_ends
    ) +
   xlim(2005,2023) +
   theme(legend.position="none")
```


```{r}
temp <- authors2 %>%
    filter(!duplicated(pmid)) %>% inner_join(., subset(abstracts, select=c(pmid, pub_date)), by="pmid") %>%
    group_by(country4, year=year(pub_date)) %>%
    summarise(n=n()) 
data_ends <- filter(temp, year == "2023")

temp %>%
    ggplot(., aes(x=year, y=n, colour=country4)) + 
    # geom_smooth(se=FALSE) + 
    geom_line() +
    geom_point(data=data_ends, aes(x=year, y=n, colour=country4)) +
    geom_text_repel(
        aes(label = country4), data = data_ends
    ) +
   xlim(2005,2023) +
   theme(legend.position="none")
```

## Understanding the growth in China

Count abstracts based on whether the affiliation is a hospital based university

```{r}
authors2 %>% mutate(hospital = grepl("medical", institution, ignore.case=TRUE) | grepl("hospital", institution, ignore.case=TRUE)) %>%
  group_by(country4, hospital) %>% count()
```

```{r}
authors2 %>% mutate(hospital = grepl("medical", institution, ignore.case=TRUE) | grepl("hospital", institution, ignore.case=TRUE)) %>%
  group_by(country2, hospital) %>% count()
```


Which medical universities have the most abstracts?

```{r}
authors %>% mutate(hospital = grepl("medical", institution, ignore.case=TRUE) | grepl("hospital", institution, ignore.case=TRUE)) %>% filter(hospital, country == "China") %>% group_by(institution) %>% count() %>% arrange(desc(n))
```

```{r}
authors2$country5 <- authors2$country2
authors2 <- authors2 %>% mutate(hospital = grepl("medical", institution, ignore.case=TRUE) | grepl("hospital", institution, ignore.case=TRUE))
authors2$country5[authors2$country2 == "China" & authors2$hospital] <- "China (medical)"

temp <- authors2 %>%
    filter(!duplicated(pmid)) %>% inner_join(., subset(abstracts, select=c(pmid, pub_date)), by="pmid") %>%
    group_by(country5, year=year(pub_date)) %>%
    summarise(n=n()) 
data_ends <- filter(temp, year == "2023")

temp %>%
    ggplot(., aes(x=year, y=n, colour=country5)) + 
    # geom_smooth(se=FALSE) + 
    geom_line() +
    geom_point(data=data_ends, aes(x=year, y=n, colour=country5)) +
    geom_text_repel(
        aes(label = country5), data = data_ends
    ) +
   xlim(2005,2023) +
   theme(legend.position="none")
```


## Diversity

```{r}
dates <- subset(abstracts, select=c(pmid, pub_date))
authors2 <- left_join(authors2, dates, by="pmid")
authors2$year <- year(authors2$pub_date)
authors2$month <- month(authors2$pub_date)

# Get the cumulative number of countries per year
lapply(unique(authors2$year), function(x) {
    temp <- authors2 %>% filter(year <= x)
    ncountry <- n_distinct(temp$V2)
    tibble(year=x, ncountry=ncountry)
}) %>% bind_rows() %>%
ggplot(., aes(x=year, y=ncountry)) + geom_line() + geom_point() + labs(y="Cumulative number of countries", x="Year")

lapply(unique(authors2$year), function(x) {
    temp <- authors2 %>% filter(year == x)
    ncountry <- n_distinct(temp$V2)
    tibble(year=x, ncountry=ncountry)
}) %>% bind_rows() %>%
filter(year != 2025) %>%
ggplot(., aes(x=year, y=ncountry)) + geom_line() + geom_point() + labs(y="Annual number of countries contributing MR papers", x="Year")
ggsave(here("docs", "fig1d.pdf"), width=7, height=4)

```


## Manual check of the data

Something is wrong with the current ChatGPT mapping. Do a manual annotation of country affiliations.

```{r}
orig_abstracts <- jsonlite::read_json(here("data/pubmed_abstracts_20250519.json"))
orig_abstracts <- lapply(orig_abstracts, function(x) {
    as_tibble(x)
}) %>% bind_rows()

orig_abstracts$ymd <- lubridate::ymd(orig_abstracts$pub_date)
orig_abstracts$year <- year(orig_abstracts$ymd)
table(orig_abstracts$year)

table(orig_abstracts$year, is.na(orig_abstracts$ab))
table(orig_abstracts$year, is.na(orig_abstracts$author_affil))
```


```{r}
author_results <- jsonlite::read_json(here("data/pubmed_authors_20250502.json"), flatten=TRUE)
temp <- author_results[[4213]] %>% as_tibble()
temp$institution <- unlist(temp$institution)
author_results <- lapply(author_results, function(x) {
    x <- as_tibble(x)
    x$institution <- unlist(x$institution)
    x$country <- unlist(x$country)
    x
}) %>% bind_rows()

# author_results

# orig_abstracts

table(orig_abstracts$pmid %in% author_results$pmid)
table(orig_abstracts$year, orig_abstracts$pmid %in% author_results$pmid)
table(author_results$pmid %in% orig_abstracts$pmid)
```

```{r}
china <- grepl("China", orig_abstracts$author_affil, ignore.case=TRUE)
usa <- grepl("usa", orig_abstracts$author_affil, ignore.case=TRUE) |
    grepl("united states", orig_abstracts$author_affil, ignore.case=TRUE) |
    grepl("united states of america", orig_abstracts$author_affil, ignore.case=TRUE)
uk <- grepl("united kingdom", orig_abstracts$author_affil, ignore.case=TRUE) |
    grepl("UK", orig_abstracts$author_affil, ignore.case=FALSE) |
    grepl("england", orig_abstracts$author_affil, ignore.case=TRUE) |
    grepl("scotland", orig_abstracts$author_affil, ignore.case=TRUE) |
    grepl("wales", orig_abstracts$author_affil, ignore.case=TRUE)
  
all_others <- !china & !usa & !uk

sum(china)
sum(usa)
sum(uk)
sum(all_others)

country_pmids <- bind_rows(
    tibble(country="China", pmid = orig_abstracts$pmid[china]),
    tibble(country="USA", pmid = orig_abstracts$pmid[usa]),
    tibble(country="UK", pmid = orig_abstracts$pmid[uk]),
    tibble(country="All other countries", pmid = orig_abstracts$pmid[all_others])
) %>% filter(!duplicated(pmid))

orig_abstracts <- left_join(orig_abstracts, country_pmids, by = "pmid")
orig_abstracts_summary <- orig_abstracts %>%
    group_by(year, country) %>%
    summarise(n=n())

data_ends <- filter(orig_abstracts_summary, year == "2024")

orig_abstracts_summary %>%
    ggplot(., aes(x=year, y=n, colour=country)) + 
    geom_line() +
    geom_point() +
    xlim(2003,2024) +
    theme(legend.position="none") +
    geom_text_repel(aes(label = country), data = data_ends) +
    labs(y="Number of papers", x="Year") +
    theme(axis.text.x=element_text(angle=45, hjust=1))
ggsave(here("docs", "fig1a.pdf"), width=7, height=7)
```


Plot by continent

```{r}
library(readxl)
continents <- read_xlsx(here("data", "country-list.xlsx"))
continents

orig_abstracts2 <- jsonlite::read_json(here("data/pubmed_abstracts_20250519.json"))
orig_abstracts$country %>% unique() %>% sort()

orig_abstracts2 <- lapply(orig_abstracts2, function(x) {
    as_tibble(x)
}) %>% bind_rows()

author_results$country %>% unique() %>% sort()
country_mapping <- read.csv(here("data", "countries.csv"), header=F)

table(author_results$country %>% unique() %>% sort() %in% country_mapping$V1)
author_results <- left_join(author_results, country_mapping, by=c("country"="V1"))
table(author_results$V2 %in% continents$Country)
subset(author_results, !V2 %in% continents$Country)$V2 %>% unique() %>% sort()


update_names <- tribble(
~V2, ~country2,
"Czech Republic", "Czechia",
"Hong Kong", "China, Hong Kong Special Administrative Region",
"Iran", "Iran (Islamic Republic of)",
"Russia", "Russian Federation",
"South Korea", "Republic of Korea",
"The Netherlands", "Netherlands",
"United Kingdom", "United Kingdom of Great Britain and Northern Ireland",
"USA", "United States of America"
)

author_results$V3 <- update_names$country2[match(author_results$V2, update_names$V2)]
author_results$V3[is.na(author_results$V3)] <- author_results$V2[is.na(author_results$V3)]

table(author_results$V3 %in% continents$Country)
subset(author_results, !V3 %in% continents$Country)$V3 %>% unique() %>% sort()
```

```{r}
unique_countries <- unique(c(author_results$country, author_results$V2, author_results$V3)) %>% na.omit()
unique_countries <- unique_countries[! unique_countries %in% c("", "CA", "PA", "US", "SAU", "CN")]
orig_abstracts_countries <- lapply(unique_countries, \(i) {
    ind <- grepl(i, orig_abstracts$author_affil, ignore.case=TRUE)
    tibble(country=i, pmid=orig_abstracts$pmid[ind])
}) %>% bind_rows()
dim(orig_abstracts_countries)
length(unique(orig_abstracts_countries$pmid))
table(orig_abstracts_countries$country %in% author_results$country)

country_mapping2 <- subset(author_results, !duplicated(country), select=c(country, V2, V3))

orig_abstracts_countries <- left_join(orig_abstracts_countries, country_mapping2, by=c("country"="country"))
table(is.na(orig_abstracts_countries$country))

orig_abstracts_countries$V3[orig_abstracts_countries$country == "Hong Kong Special Administrative Region of China"] <- "China, Hong Kong Special Administrative Region"
orig_abstracts_countries$V3[orig_abstracts_countries$country == "Russian Federation"] <- "Russian Federation"
orig_abstracts_countries$V3[orig_abstracts_countries$country == "CHN"] <- "China"
orig_abstracts_countries$V3[orig_abstracts_countries$country == "Country"] <- NA
orig_abstracts_countries$V3[orig_abstracts_countries$country == "Indonesia"] <- "Indonesia"
orig_abstracts_countries$V3[orig_abstracts_countries$country == "Saudi Arabia"] <- "Saudi Arabia"
orig_abstracts_countries$V3[orig_abstracts_countries$country == "United Kingdom of Great Britain and Northern Ireland"] <- "United Kingdom of Great Britain and Northern Ireland"

orig_abstracts_countries <- left_join(orig_abstracts_countries, continents, by=c("V3"="Country"))
table(is.na(orig_abstracts_countries$continent))

subset(orig_abstracts_countries, is.na(continent))$country %>% unique() %>% sort()

str(orig_abstracts_countries)

orig_abstracts2j <- left_join(orig_abstracts %>% select(-country), orig_abstracts_countries, by="pmid")
dim(orig_abstracts2j)

orig_abstracts2j_collapsed <- orig_abstracts2j %>% group_by(pmid) %>%
    summarise(
        year=first(year),
        country = paste(sort(unique(na.omit(V3))), collapse="; "),
        continent = paste(sort(unique(na.omit(continent))), collapse="; "),
        region1 = paste(sort(unique(na.omit(region1))), collapse="; ")
    )




orig_abstracts_summary_continent_col <- orig_abstracts2j_collapsed %>%
    filter(!is.na(continent)) %>%
    group_by(year, country=continent) %>%
    summarise(n=n())

orig_abstracts_summary_continent <- orig_abstracts2j %>%
    filter(!is.na(continent)) %>%
    group_by(year, country=continent) %>%
    summarise(n=n())

orig_abstracts_summary_region <- orig_abstracts2j %>%
    filter(!is.na(continent)) %>%
    group_by(year, country=region1) %>%
    summarise(n=n())



data_ends_continent_col <- filter(orig_abstracts_summary_continent_col, year == "2024")
data_ends_continent <- filter(orig_abstracts_summary_continent, year == "2024")
data_ends_region <- filter(orig_abstracts_summary_region, year == "2024")

orig_abstracts_summary_continent %>%
    ggplot(., aes(x=year, y=n, colour=country)) + 
    geom_line() +
    geom_point() +
    xlim(2003,2024) +
    theme(legend.position="none") +
    geom_text_repel(aes(label = country), data = data_ends_continent) +
    labs(y="Number of papers", x="Year") +
    theme(axis.text.x=element_text(angle=45, hjust=1))

orig_abstracts_summary_region %>%
    ggplot(., aes(x=year, y=n, colour=country)) + 
    geom_line() +
    geom_point() +
    xlim(2003,2024) +
    theme(legend.position="none") +
    geom_text_repel(aes(label = country), data = data_ends_region) +
    labs(y="Number of papers", x="Year") +
    theme(axis.text.x=element_text(angle=45, hjust=1)) +
    scale_y_log10()

orig_abstracts_summary_continent %>%
    ggplot(., aes(x=year, y=n, colour=country)) + 
    geom_line() +
    geom_point() +
    xlim(2003,2024) +
    theme(legend.position="none") +
    geom_text_repel(aes(label = country), data = data_ends_continent) +
    labs(y="Number of papers", x="Year") +
    theme(axis.text.x=element_text(angle=45, hjust=1)) +
    scale_y_log10()

pmids_to_check <- subset(orig_abstracts2j_collapsed, continent == "Asia; North America")$pmid

affils <- orig_abstracts2$author_affil[orig_abstracts2$pmid %in% pmids_to_check]

affils[1]

for(i in unique_countries) {
    if(grepl(i, affils[1], ignore.case=TRUE, )) print(i)
}


```

```{r}
region_sizes <- tribble(
    ~region1, ~pop,
    "Southern Asia",	1989452478,
    "Northern Europe",	106197357,
    "Southern Europe",	152130606,
    "Northern Africa",	255737736,
    "Polynesia",	717467,
    "Middle Africa",	190267973,
    "Caribbean",	656098097,
    "Antarctica",	0,
    "South America",	434254119,
    "Western Asia",	289733123,
    "Australia and New Zealand",	31050816,
    "Western Europe",	195381649,
    "Eastern Europe",	291464162,
    "Central America",	177661929,
    "Western Africa",	418544337,
    "Northern America",	375278947,
    "Southern Africa",	67984554,
    "Eastern Africa",	461141845,
    "South-eastern Asia",	675796065,
    "Eastern Asia",	1663696923,
    "Melanesia",	12188834,
    "Micronesia",	534606,
    "Central Asia",	75897577
)

orig_abstracts_summary_region_size <- left_join(orig_abstracts_summary_region, region_sizes, by=c("country"="region1")) %>%
    mutate(n_per_million = n / (pop / 1e6))
data_ends_region <- filter(orig_abstracts_summary_region_size, year == "2024")

orig_abstracts_summary_region_size %>%
    ggplot(., aes(x=year, y=n_per_million, colour=country)) + 
    geom_line() +
    geom_point() +
    xlim(2003,2024) +
    theme(legend.position="none") +
    geom_text_repel(aes(label = country), data = data_ends_region) +
    labs(y="Number of papers per 1 million population size", x="Year") +
    theme(axis.text.x=element_text(angle=45, hjust=1))
ggsave(here("docs", "fig1ap.pdf"), width=7, height=7)
```
